Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-02-20 paper/snakemajoranas.tex
finish review Sec III

\comment{We discretize the Hamiltonian and simulate it with Kwant.}
We discretize our continuum Hamiltonian [Eq.~\eqref{eq:hamiltonian}] on a square grid and implement a tight-binding model using Kwant~\cite{groth_kwant:_2014}.
To optimize the sampling in important regions of parameter space, we use the Adaptive package.~\cite{adaptive}
The entire source code and the resulting raw data are available in Ref.~\onlinecite{data}.  % TODO: update the bib when the data is uploaded

@@

\comment{We calculate the band structure for varying amount of zigzag.}
We diagonalize the supercell Hamiltonian to compute the band structure.
Because of the large periodicity of the zigzag and the resulting large supercell, the band structure is heavily folded.
In figure~\ref{fig:band_stuctures} we show the resulting band structures for zigzag systems with a varying amplitude.

\comment{The band structures show that modulation of the geometry increases the gap by an order of magnitude, as well as reduce the group velocity.}
The introduction of a zigzag has a striking effect: the bands flatten out and the topological gap increases by more than an order of magnitude.
On an intuitive level we can understand this because in a straight system long trajectories are possible, these have a momentum that is directed along the strip and consequently, $k_x \approx k_F$.
Further, the smallest gap in a straight system occurs around $k_F$, and because the zigzag cuts off long trajectories, the gap size increases.
Besides this, the states that exist in different segments have very little overlap and therefore have a very small velocity.
This reduction in velocity has a positive effect on the Majorana coherence length, as described later in section \ref{sec:shape_effects}.

\comment{The introduction of an NS interface at many angles increases the transparency.}
Additionally, in the presence of normal reflection, due to the presence of NS interfaces at a wide range of angles, the reflected part will eventually scatter with a near perpendicular surface.
This means that for transversal modes the transparency of the NS interface will increase.

>>>>

\comment{We discretize the Hamiltonian and simulate it with Kwant.}
We discretize our continuum Hamiltonian [Eq.~\eqref{eq:hamiltonian}] on a square grid and implement a tight-binding model using Kwant~\cite{groth_kwant:_2014}.
To preferentially sample important regions of parameter space, we use the Adaptive package.~\cite{adaptive}
The entire source code and the resulting raw data are available in Ref.~\onlinecite{data}.  % TODO: update the bib when the data is uploaded

@@

\comment{We calculate the band structure for varying amount of zigzag.}
We apply sparse diagonalization to the supercell Hamiltonian at different momenta $k_x$ to compute the band structure.
Because of the large periodicity of the zigzag and the resulting large supercell, the band structure is heavily folded.
In figure~\ref{fig:band_stuctures} we show the resulting band structures for zigzag systems with a varying amplitude.
The introduction of the zigzag has a striking effect: the bands flatten out and the topological gap increases by more than an order of magnitude.

\comment{Zigzag improves the gap and size because of cutting of trajectories and increasing transparency.}
This confirms our expectation that the zigzag removes trajectories propagating at grazing angles.
In the unfolded band structure for a straight system, as seen in Fig.~\ref{fig:bandstructures}(a), the gap in a straight system occurs around $k_F$ and because the zigzag cuts off long trajectories, the gap size increases.
Besides this, the states from different segments of the zigzag pattern have a negligible overlap and therefore have a vanishing velocity.
This reduction in velocity strongly reduces the Majorana size, as we discuss in section \ref{sec:shape_effects}.
Additionally, in the presence of normal reflection, due to the presence of NS interfaces at a wide range of angles, the reflected part eventually scatters with a near perpendicular surface.
This means that for transversal modes the transparency of the NS interface increases.
